Make any stupid plot you want

### 2021-02-14 draft/sections/next.tex
- existential crisis on what is next?
I can has no idea

\subsection{What are the limitations?}
Is not useful for much yet.

@@

\subsection{What are the lessons learned?}

>>>>

\subsection{What have we done}
presented mathematical framework w/ topological models for the things we have done. 
 \begin{itemize}
    \item fiberbundle -> continuity + variables
    \item fiberbundle -> graphic continuity + display abstraction
    \item formalizing equivariance on both sides 
    \item prototype for scatter, line, bar
    \item simple composition into multibar
    \item commonly used container - dataframe
 \end{itemize}

\subsection{What are the limitations?}
This framework is aimed at developers, not end users which is why it's equation soup only understood by physicits and mathematicians.

.  It is a way to describe the pathway from data to graphic in a

@@

Other things that may or may not play a big role would be working out the details of the S->K interaction for dashboards. By this I particularly mean when S is a composite object spanning all the figures shown in the dashboard and a component of K may have different compoents of S mapping into it slicing it in different ways.
\subsection{What are the lessons learned?}
